\documentclass[languages_and_machines.tex]{subfiles}
\begin{document}


\begin{frame}
  \frametitle{Turing Machines equivalents}

  \begin{itemize}
  \item Modern computers (within memory limitations)
    \pause
  \item Arbitrary grammar
    \pause
  \item Recursively enumerable (composition, recursion, `count-up')
    \pause
  \item FRACTRAN
    \pause
  \item Lambda Calculus
    \pause
  \item FlooP
  \end{itemize}

  None of these are guaranteed to halt!

\end{frame}

\begin{frame}
  \frametitle{P \only<1>{=}\only<2>{\(\neq\)} NP}

  Deterministic TM \textbf{P}olynomial-time algorithm
  \only<1>{\(\iff\)}\only<2>{\(\hspace{1.5ex}\not\hspace{-2ex}\iff\)}
  \textbf{N}on-deterministic TM \textbf{P}olynomial-time algorithm?
\end{frame}

\begin{frame}
  \frametitle{Universal Turing Program}

  Turing Machine takes encoding of a machine and its input, separated by a marker symbol.

  Decides if machine accepts given input.
\end{frame}

% \begin{frame}
%   \frametitle{DTM \(\iff\) NTM}

%   Backtracking
% \end{frame}

\begin{frame}
  \frametitle{Unrestricted Grammars}

  \(\alpha \to \beta\)

  \(\alpha\) and \(\beta\) can be anything in \((\Gamma \cup \Sigma)^*\)!
\end{frame}

\begin{frame}
  \frametitle{Unrestricted Grammars \(\iff\) NTM}

  Task: construct NTM that recognizes strings genreated by an unrestricted grammar

  \(x_0 x_1 \dotsb x_n\) on tape.

  \pause

  Append \(\# S\).

  \pause

  Start simulating a derivation, replacing \(\alpha\) with \(\beta\) according to grammar. Result is unbounded, but so is tape.

  \pause

  If string before \# matches that after, accept.

  \pause

  \textbf{Could take forever}
\end{frame}

\begin{frame}
  \frametitle{Unrestricted Grammars \(\iff\) NTM}

  \(x_0 x_1 \dotsb x_n\) \\
  \pause
  \(x_0 x_1 \dotsb x_n \# S\) \\
  \pause
  \(x_0 x_1 \dotsb x_n \# \alpha \gamma\) \\
  \pause
  \(x_0 x_1 \dotsb x_n \# \beta \theta \gamma \alpha\) \\
  \pause
  \(\vdots\) \\
  \pause
  \(x_0 x_1 \dotsb x_n \# x_1 x_2 \dotsb x_n\) \\
  \pause
  accept
\end{frame}

\begin{frame}
  \frametitle{Unrestricted Grammars \(\iff\) NTM}

  Suppose \(\textcolor{green}{(S_i', x_n', L)} \in \textcolor{red}{f(S_i, x_n)}\),

  then \(\textcolor{red}{S_i' x_{n-1} x_n'} \to \textcolor{green}{x_{n-1} S_i x_n}\).

\end{frame}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
